Flatiron cleaning

### 2022-03-31 Rmd/Actual weight rdi analysis.Rmd
Simplify Rmd: transfer stable code for drugs cleaning in R script 02.data cleaning and call the cleaned rds in the Rmd

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
Look at the Cox regression model before imputation.

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os_from_treatment"] <- 0
Pred
```

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
pool(check1)$pooled
```

Do m = 34 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.339 that we multiply by 100)
```{r}
hggjgjgkj change the m number
Cox.imp <- mice(dataset, m=34, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.

### For Upfront Surgery
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os_from_treatment"] <- 0
Pred
```

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
pool(check1)$pooled
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

>>>>

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
Look at the Cox regression model before imputation.

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os, vital_status)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os"] <- 0
Pred
```

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
pool(check1)$pooled
```

Do m = 34 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.339 that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m=34, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.

### For Upfront Surgery
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os, vital_status)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os"] <- 0
Pred
```

@@

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
pool(check1)$pooled
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
